### 2024-06-28 conteudo/methods/methods.tex
add random selection of ethnografy

@@

>>>>

\label{subsec:pipeline}

@@

As discussed in the empyrical analyses for the tool, it is impractical to evaluate every code duplication on Linux kernel. Thus,
similarily to the empyrical analyses for the tool, we will limit the experiment scope to only the AMD Display driver and select
a random sample of duplicated functions infered by our tool to initiate the mitigation approach defined in \ref{subsec:pipeline}. 
We chose a sample size of 30 duplicated functions, as there are multiples studies demonstrated that a sample size of this size 
have a statistical significance \citep{sample1,sample2}.

On the the random selection of the duplicated functions, we deside to put a additional restriction on which functions pairs are 
elegible to be selected. The restriction is that we will only select functions pairs with similarity metric equal 
to 100\%, we made this choice because, as showed in the Figure \ref{fig:relatory_ex}, there are more then 20,000 lines codes 
in the AMD Display driver in which the similarity metric reaches this value. On all function pairs that respect the restriction,
we will choose then uniformly at random.

The functions pairs selected at random following our methodoly can be consulted in the Table (CREATE TABLE AND ADD HERE).

CREATE TABLE AND ADD HERE.
